---
title: "My First Markdown"
author: "Kyle Kozelsky"
date: "9/14/2019"
output: html_document
---

Bold - **bold**  
Italics - _Italics_  
Italics other way - *Italics*  
Bold and Italics - _**Wow**_  

# Title  
## Subtitle
### Section Title
#### Subsection Title  

- Bullet List 1
- Bullet List 2
- Bullet List 3

* Bullet List 1
* Bullet List 2
* Bullet List 3

1. Ordered List 1
1. Ordered List 2
1. Ordered List 3

Add something in between to start the count over

1. Ordered List 1a
1. Ordered List 2a
1. Ordered List 3a

##ggplot

```{r first_chunk}
gapminder <- read.table("gapminder.txt", header = TRUE)
head(gapminder)
```

```{r Challenge1, fig.height=5, fig.width=7}
library(ggplot2)

az_row <- startsWith(as.vector(gapminder$country), c('A','Z'))
az_countries <- gapminder[az_row,]

ggplot(data = az_countries, aes(x = year, y = lifeExp, color=continent)) +
  geom_line() + facet_wrap( ~ country) +
  labs(
    x = "Year",              # x axis title
    y = "Life expectancy",   # y axis title
    title = "Figure 1",      # main title of figure
    color = "Continent"      # title of legend
  ) +
  theme(axis.text.x=element_text(angle=45), axis.ticks.x=element_blank())
```

The mean life expectancy of Sweden is `r mean(gapminder[gapminder$country=="Sweden", "lifeExp"])`.

